systemfit: A Package to Estimate\\ Simultaneous Equation Systems in \proglang{R}

### 2006-02-28 paper/trunk/systemfit_other.tex
modified discussion about centering the residuals before calculating its covariance matrix; added description of new argument "CenterResiduals"; modified replication of residual covariance matrix in Greene (2003), Table 14.1 (p. 351) and errata.
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/systemfit@653 591db2bd-e0a0-4d22-8c19-2192dbb7da31

In some uncommon cases,
for instance in pooled estimations,
where the coefficients are restricted to be equal in all equations,
the means of the residuals of each equation are not equal to zero
$( \overline{ \widehat{u} }_i \neq 0 )$.
Therefore, we subtract the means from the residuals
and substitute $\widehat{u}_i - \overline{ \widehat{u} }_i$
for $\widehat{u}_i$ in (\ref{eq:rcov0}--\ref{eq:rcov2}).

>>>>

In some uncommon cases,
for instance in pooled estimations,
where the coefficients are restricted to be equal in all equations,
the means of the residuals of each equation are not equal to zero
$( \overline{ \widehat{u} }_i \neq 0 )$.
Therefore, it might be argued
that the residual covariance matrix should be calculated
by subtracting the means from the residuals
and substituting $\widehat{u}_i - \overline{ \widehat{u} }_i$
for $\widehat{u}_i$ in (\ref{eq:rcov0}--\ref{eq:rcov2}).
